Forecasting the 2024 US Presidential Election

### 2024-11-04 paper/paper.qmd
Makes further edits of the paper's qmd to fix errors (wording, being more specific, prose, etc.), mostly in discussions and Appendix A.

Our model provides insightful predictions on the 2024 U.S. presidential election landscape, highlighting both the strengths and potential uncertainties within the swing states. By examining the demographic and historical predictors, we observed significant patterns in voter leanings and demographic shifts, particularly in critical swing states such as Georgia, Michigan, and Pennsylvania. The model suggests that minor shifts in demographics or campaign focus within these states could lead to substantial impacts on the election outcome. For example, Georgia, which exhibits an almost even split in party leanings, underscores the importance of targeted outreach to specific demographics, like college-educated voters and minority groups, which show slight inclinations towards the Democratic party.

@@

# Appendix {#sec-appendix-A}

## Pollster Methodology Overview {-}
Emerson College Polling was initially a college polling exercise and is now an "innovative, nationally-ranked" non-partisan polling center (@AboutUs). For the 2024 USA Presidential Election pollster, the Emerson College Polling defined the population to be "likely voters" of 2024 United States Presidential Election. Emerson College Polling does indicate that the targeted population of "likely voters" is based on "2024 Likely Voter Modeling." However, the methodology for this modelling and the specific model is not indicated, so we can't determine the scope of the targeted population (@Polling).

Emerson College Polling recruits people completing this survey for this national pollster by contacting mobile phones using "MMS-to-Online", "Online Opt-in Panel", and "IVR(Interactive Voice Response)" (@Polling). In the MMS-to-Online approach, the target population were sent text messages with graphics that invite them to take a "screening questionnaire", and those who pass the questionnaire can move on to take the survey. The selected respondents were based on state voter files "provided by Aristotle." The Online Opt-in Panel approach involves respondents from the targeted population being invited to finish the survey by means of an online opt-in panel "provided by CINT" (@AboutUs). Specifically, in the Online Panel approach, selected voters were pre-matched to "L2 voter file data provided by Rep Data" (@Polling). Finally, the IVR approach involves making automatic telephone calls to selected "likely voters." Participants then answer the survey using their "touch-tone telephone". The email approach indicated in Emerson College Polling's official methodology (@AboutUs) is not mentioned in the National Polling, so it can be assumed that this approach is not used in our chosen pollster data.

From the methodology of recruiting people indicated in the previous paragraph, we can see that while the targeted population of the national poll are likely voters, the sampling frame are likely voters that use phones, either mobile or landline. Emerson College Polling chooses 1000 samples from their targeted population of likely voters of the 2024 United States Presidential Election, and it is then "weighted by gender, education, race, age, party affiliation, and region based on 2024 likely voter modeling" (@Polling) for each national poll. As most people in the United States use phones by some means, the target population and sampling frame are highly similar, increasing the overall validity of the survey.

>>>>

Our model provides insightful predictions on the 2024 U.S. presidential election landscape, highlighting both the strengths and potential uncertainties within the swing states, and ultimately providing predictions of results of the 2024 United States of America Presidential Elections. By examining the demographic and historical predictors, we observed significant patterns in voter leanings and demographic shifts, particularly in critical swing states such as Georgia, Michigan, and Pennsylvania. The model suggests that minor shifts in demographics or campaign focus within these states could lead to substantial impacts on the election outcome. For example, Georgia, which exhibits an almost even split in party leanings, underscores the importance of targeted outreach to specific demographics, like college-educated voters and minority groups, which show slight inclinations towards the Democratic party.

@@

# Appendix: Pollster Methdology Overview - Weaknesses and Potential Improvements{#sec-appendix-A}

Emerson College Polling initially developed from a classroom polling exercise and is now an "innovative, nationally-ranked" non-partisan polling center (@AboutUs). For the 2024 USA Presidential Election pollster, the Emerson College Polling defined the population to be "likely voters" of 2024 United States Presidential Election. Emerson College Polling does indicate that the targeted population of "likely voters" is based on "2024 Likely Voter Modeling." However, the methodology for this modeling and the specific model is not indicated, so we can not determine the scope of the targeted population (@Polling).

Emerson College Polling recruits people completing this survey for this national pollster by contacting mobile phones using "MMS-to-Online", "Online Opt-in Panel", and "IVR(Interactive Voice Response)" (@Polling). In the MMS-to-Online approach, the target population were sent text messages with graphics that invite them to take a "screening questionnaire", and those who pass the questionnaire can move on to take the survey. The selected respondents were based on state voter files "provided by Aristotle." The Online Opt-in Panel approach involves respondents from the targeted population being invited to finish the survey by means of an online opt-in panel "provided by CINT" (@AboutUs). Specifically, in the Online Panel approach, selected voters were pre-matched to "L2 voter file data provided by Rep Data" (@Polling). Finally, the IVR approach involves making automatic telephone calls to selected "likely voters." Participants then answer the survey using their "touch-tone telephone". The email approach indicated in Emerson College Polling's official methodology (@AboutUs) is not mentioned in the National Polling (@Polling), so it can be assumed that this approach is not used in our chosen pollster data.

From the methodology of recruiting people indicated in the previous paragraph, we can see that while the targeted population of the national poll are likely voters, the sampling frame are likely voters that use phones, either mobile or landline. Here, note that the definition of likely voters is set by Emerson College Polling, and the datasets where each sample is chosen from is described in the three approaches by Emerson's methodologies. Emerson College Polling chooses 1000 samples from their targeted population of likely voters of the 2024 United States Presidential Election, and it is then "weighted by gender, education, race, age, party affiliation, and region based on 2024 likely voter modeling" for each national poll. As most people in the United States use phones by some means, the target population and sampling frame are highly similar, increasing the overall validity of the survey.
